Tailoring Differentially Private Bayesian Inference to Distance Between Distributions

### 2018-10-26 Arxiv/main.tex
rewrite differential privacy other cases

\begin{definition}
\label{def_cardinality}
  $\cardinality{r}$

  Define $\cardinality{r}$ as the cardinality of $R_r$ s.t. $ R_r = \{ r' | r' \in \candidateset{\dataobs}\ s.t. \ \ux{r'} = \ux{r}, \}$ and $\forall \hat{r} \in \candidateset{\dataobs}, \hat{r} \notin R_r \implies \ux{\hat{r}} \neq \ux{r}$, 
\end{definition}

\begin{lem}
\label{lem_score_pro_convert}
 Given $\hexpmech(\dataobs)$, then the following property holds:
\begin{equation*}
\hexpmechPr{\dataobs}{\ux{z} = \ux{r}} = \cardinality{r}\hexpmechPr{\dataobs}{z = r}
 \end{equation*}
\end{lem}
\begin{proof} of Lemma \ref{lem_score_pro_convert}.\\
To compute $\hexpmechPr{\dataobs}{\ux{z} = \ux{r}}$\\
$\iff $ to compute $\hexpmechPr{\dataobs}{ R | R = \{r' | r' \in \candidateset{\dataobs} \land \ux{r'} = \ux{r}\}}.$\\
By Definition \ref{def_cardinality}, $R_r$ is this set.\\
$\implies \hexpmechPr{\dataobs}{\ux{z} = \ux{r}} = \hexpmechPr{\dataobs}{R_r} $.\\
By the independence of $r' \in R_r$, $ \hexpmechPr{\dataobs}{z \in R_r}  =\sum\limits_{r'\in R_r} \hexpmechPr{\dataobs}{z = r'}$ ,\\
Apply Lemma \ref{lem_score_pro_eq} in $R_r$, \\
$\implies$ for any $r', r''\in R_r$, $\hexpmechPr{\dataobs}{z = r'} = \hexpmechPr{\dataobs}{z = r''}$.\\
$\implies$ $\sum\limits_{r'\in R_r} \hexpmechPr{\dataobs}{z = r'} = \cardinality{r}\hexpmechPr{\dataobs}{z = r}$.\\
$\implies$ $\hexpmechPr{\dataobs}{\ux{z} = \ux{r}} = \cardinality{r}\hexpmechPr{\dataobs}{z = r}$.\\
\end{proof}

@@

In Beta-binomial system, $\cardinality{r}$ takes two possible value: $1$, $2$:
\begin{itemize}
  \item[-] $\cardinality{r} = 1$, $\ux{r} = 0$,  containing only the correct posterior.
  \item[-] $\cardinality{r} = 2$, $\ux{r} \neq 0$. $R_r$ containing 2 elements by the symmetry property of $\hellinger$.
\end{itemize}

\todo{
In Beta-binomial system, $\cardinality{r}$ takes two possible value: $1$, $2$. Let $\mathcal{R}_1$, $\mathcal{R}_2$ be a partition of $\candidateset{\dataobs}$:
\begin{itemize}
  \item[*] $\mathcal{R}_1 = \{r | r \in \candidateset{\dataobs}\ s.t.\ \cardinality{r} = 1\}$.
  \item[*] $\mathcal{R}_2 = \{r | r \in \candidateset{\dataobs}\ s.t.\ \cardinality{r} = 2\}$.
\end{itemize}
}

Let $\ux{t} = \ux{r} + k$. The proof is given by cases:
\begin{itemize}
  \item $\ux{r} \neq 0$, $\ux{r} + k \neq 0$. \todo{$r \in \mathcal{R}_2 \land t \in \mathcal{R}_2$} \\
  By $\ux{r} + k \neq 0$, $\cardinality{t} = 2$. \todo{By $t \in \mathcal{R}_2$, $\cardinality{t} = 2$}\\
  By $\ux{r} \neq 0 $, $\cardinality{r} = 2$. \todo{By $r \in \mathcal{R}_2$, $\cardinality{r} = 2$}\\
  Destruct k:
  \begin{itemize}
    \item  $k \geq 0$: $\implies$\\
      \begin{equation*}
      \begin{split}
      LHS 
      & = \cardinality{r} \cdot \hexpmechPr{\dataobs}{z = r}     (Apply\ Lemma\ \ref{lem_score_pro_convert})\\
      & = \cardinality{r} \cdot \frac {exp\big(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs),r)}{2\cdot S(\dataobs)}\big)}{\nomalizer{\dataobs}} 
      (Apply\ Definition\ \ref{def_smoo})\\
      & = \cardinality{r} \cdot \frac{exp(\frac{-\epsilon \ux{r}}{2 S(\dataobs)})}{\unomalizer{\dataobs}}
      (Apply\ \ux{r} = \hellinger(\bysinfer(\dataobs), r))\\
      & = 2 \cdot \frac{exp(\frac{-\epsilon \ux{r}}{2 S(\dataobs)})}{\unomalizer{\dataobs}}                  (Apply\ \cardinality{r} = 2)\\
      & = 2 \cdot \frac{exp(\frac{-\epsilon (\ux{r} + k - k)}{2 S(\dataobs)})}{\unomalizer{\dataobs}}\\
      & = 2 \cdot \frac{exp(\frac{-\epsilon (\ux{r} + k)}{2 S(\dataobs)} + \frac{\epsilon k}{2 S(\dataobs)})}{\unomalizer{\dataobs}}\\
      & = 2 \cdot \frac{exp(\frac{-\epsilon (\ux{r} + k)}{2 S(\dataobs)})}{\unomalizer{\dataobs}} \cdot e^{\frac{\epsilon k}{2 S(\dataobs)}}\\
      & = 2 \cdot \frac{exp(\frac{-\epsilon (\ux{t})}{2 S(\dataobs)})}{\unomalizer{\dataobs}} \cdot e^{\frac{\epsilon k}{2 S(\dataobs)}}  (Apply \ \ux{t} = \ux{r} + k)\\
      & = e^{\frac{\epsilon k}{2 S(\dataobs)}} \cdot 2 \cdot \frac {exp\big(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs), t)}{2\cdot S(\dataobs)}\big)}{\nomalizer{\dataobs}} 
      (Apply\ \ux{r} = \hellinger(\bysinfer(\dataobs), r))\\
      & = e^{\frac{\epsilon k}{2 S(\dataobs)}} \cdot 2 \hexpmechPr{\dataobs}{z = t}       (Apply\ Definition\ \ref{def_smoo})\\
      & = e^{\frac{\epsilon k}{2 S(\dataobs)}} \cdot \cardinality{t} \hexpmechPr{\dataobs}{z = t}         (Apply \ \cardinality{t} = 2)\\
      & = e^{\frac{\epsilon k}{2 S(\dataobs)}} \cdot \hexpmechPr{\dataobs}{\ux{z} = \ux{t}}               (Apply \ Lemma\ \ref{lem_score_pro_convert})\\
      & = e^{\frac{\epsilon k}{2 S(\dataobs)}} \cdot \hexpmechPr{\dataobs}{\ux{z} = (\ux{r} + k)}         (Apply \ \ux{t} = \ux{r} + k)\\
      & \leq e^{(\frac{\epsilon k}{2 S(\dataobs)} + \ln 2)} \hexpmechPr{\dataobs}{\ux{z} = (\ux{r} + k)}\\
      & = RHS.
      \end{split}
      \end{equation*}

@@

      \begin{equation*}
      \begin{split}
      LHS 
      & = \cardinality{r} \cdot \hexpmechPr{\dataobs}{z = r}     (Apply\ Lemma\ \ref{lem_score_pro_convert})\\
      & = \cardinality{r} \cdot \frac {exp\big(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs),r)}{2\cdot S(\dataobs)}\big)}{\nomalizer{\dataobs}} 
      (Apply\ Definition\ \ref{def_smoo})\\
      & = \cardinality{r} \cdot \frac{exp(\frac{-\epsilon \ux{r}}{2 S(\dataobs)})}{\unomalizer{\dataobs}}
      (Apply\ \ux{r} = \hellinger(\bysinfer(\dataobs), r))\\
      & = 2 \cdot \frac{exp(\frac{-\epsilon \ux{r}}{2 S(\dataobs)})}{\unomalizer{\dataobs}}                  (Apply\ \cardinality{r} = 2)\\
      & = 2 \cdot \frac{exp(\frac{-\epsilon (\ux{r} + k - k)}{2 S(\dataobs)})}{\unomalizer{\dataobs}}\\
      & = 2 \cdot \frac{exp(\frac{-\epsilon (\ux{r} + k)}{2 S(\dataobs)} + \frac{\epsilon k}{2 S(\dataobs)})}{\unomalizer{\dataobs}}\\
      & = 2 \cdot \frac{exp(\frac{-\epsilon (\ux{r} + k)}{2 S(\dataobs)})}{\unomalizer{\dataobs}} \cdot e^{\frac{\epsilon k}{2 S(\dataobs)}}\\
      & = 2 \cdot \frac{exp(\frac{-\epsilon (\ux{t})}{2 S(\dataobs)})}{\unomalizer{\dataobs}} \cdot e^{\frac{\epsilon k}{2 S(\dataobs)}}  (Apply \ \ux{t} = \ux{r} + k)\\
      & = e^{\frac{\epsilon k}{2 S(\dataobs)}} \cdot 2 \cdot \frac {exp\big(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs), t)}{2\cdot S(\dataobs)}\big)}{\nomalizer{\dataobs}} 
      (Apply\ \ux{r} = \hellinger(\bysinfer(\dataobs), r))\\
      & = e^{\frac{\epsilon k}{2 S(\dataobs)}} \cdot 2 \hexpmechPr{\dataobs}{z = t}       (Apply\ Definition\ \ref{def_smoo})\\
      & = e^{\frac{\epsilon k}{2 S(\dataobs)}} \cdot \cardinality{t} \hexpmechPr{\dataobs}{z = t}         (Apply \cardinality{t} = 2)\\
      & = e^{\frac{\epsilon k}{2 S(\dataobs)}} \cdot \hexpmechPr{\dataobs}{\ux{z} = \ux{t}}               (Apply \ Lemma\ \ref{lem_score_pro_convert})\\
      & = e^{\frac{\epsilon k}{2 S(\dataobs)}} \cdot \hexpmechPr{\dataobs}{\ux{z} = (\ux{r} + k)}         (Apply \ \ux{t} = \ux{r} + k)\\
      & \leq e^{(\frac{\epsilon k}{2 S(\dataobs)} + \ln 2)} \hexpmechPr{\dataobs}{\ux{z} = (\ux{r} + k)}\\
      & = RHS.
      \end{split}
      \end{equation*}

@@

  \item $\ux{r} = 0, \ux{r} + k \neq 0$. \todo{$r \in \mathcal{R}_1 \land t \in \mathcal{R}_2$}\\
        By $\ux{r} = 0$, $\cardinality{r} = 1$. \todo{By $r \in \mathcal{R}_1$, $\cardinality{t} = 1$}\\
        By $\ux{r} + k = k \neq 0$, $\cardinality{t} = 2$. \todo{By $t \in \mathcal{R}_2$, $\cardinality{t} = 2$}\\
        $\implies$\\
        \begin{equation*}
        \begin{split}
        LHS 
        & = \cardinality{r} \cdot \hexpmechPr{\dataobs}{z = r}     (Apply\ Lemma\ \ref{lem_score_pro_convert})\\
        & = \cardinality{r} \cdot \frac {exp\big(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs),r)}{2\cdot S(\dataobs)}\big)}{\nomalizer{\dataobs}} 
        (Apply\ Definition\ \ref{def_smoo})\\
        & = \cardinality{r} \cdot \frac{exp(\frac{-\epsilon \ux{r}}{2 S(\dataobs)})}{\unomalizer{\dataobs}}
        (Apply\ \ux{r} = \hellinger(\bysinfer(\dataobs), r))\\
        & = \frac{exp(\frac{- \epsilon \ux{r}}{2 S(\dataobs)})}{\unomalizer{\dataobs}}                        (Apply \ \cardinality{r} = 1) \\
        & = \frac{exp(\frac{- \epsilon (\ux{r} + k - k)}{2 S(\dataobs)})}{\unomalizer{\dataobs}}\\
        & = \frac{exp(\frac{- \epsilon (\ux{r} + k)}{2 S(\dataobs)} + \frac{\epsilon k}{2 S(\dataobs)})}{\unomalizer{\dataobs}}\\
        & = \frac{exp(\frac{-\epsilon (\ux{r} + k)}{2 S(\dataobs)})}{\unomalizer{\dataobs}} \cdot e^{\frac{\epsilon k}{2 S(\dataobs)}}\\
        & = \frac{exp(\frac{-\epsilon (\ux{t})}{2 S(\dataobs)})}{\unomalizer{\dataobs}} \cdot e^{\frac{\epsilon k}{2 S(\dataobs)}}  (Apply \ \ux{t} = \ux{r} + k)\\
        & = e^{\frac{\epsilon k}{2 S(\dataobs)}} \cdot \frac {exp\big(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs), t)}{2\cdot S(\dataobs)}\big)}{\nomalizer{\dataobs}} 
        (Apply\ \ux{r} = \hellinger(\bysinfer(\dataobs), r))\\
        & = e^{\frac{\epsilon k}{2 S(\dataobs)}} \cdot \hexpmechPr{\dataobs}{z = t}       (Apply\ Definition\ \ref{def_smoo})\\
        & < 2 \cdot e^{\frac{\epsilon k}{2 S(\dataobs)}} \cdot \hexpmechPr{\dataobs}{z = t}\\
        & = e^{\frac{\epsilon k}{2 S(\dataobs)}} \cdot \cardinality{t} \hexpmechPr{\dataobs}{z = t}   (Apply \ \cardinality{t} = 2)\\
        & = e^{\frac{\epsilon k}{2 S(\dataobs)}} \cdot \hexpmechPr{\dataobs}{\ux{z} = \ux{t}}         (Apply \ Lemma\ \ref{lem_score_pro_convert})\\
        & = e^{\frac{\epsilon k}{2 S(\dataobs)}} \cdot \hexpmechPr{\dataobs}{\ux{z} = (\ux{r} + k)}   (Apply \ \ux{t} = \ux{r} + k)\\
        & \leq e^{(\frac{\epsilon k}{2 S(\dataobs)} + \ln 2)} \hexpmechPr{\dataobs}{\ux{z} = ( \ux{r} + k)}\\
        & = RHS.
        \end{split}
        \end{equation*}

>>>>

\begin{definition}
\label{def_cardinality}
  $\cardinality{\dataobs}{r}$

  Define $\cardinality{\dataobs}{r}$ as the cardinality of $R_r$ s.t. $ R_r = \{ r' | r' \in \candidateset{\dataobs}\ s.t. \ \ux{r'} = \ux{r}, \}$ and $\forall \hat{r} \in \candidateset{\dataobs}, \hat{r} \notin R_r \implies \ux{\hat{r}} \neq \ux{r}$, 
\end{definition}

\begin{lem}
\label{lem_score_pro_convert}
 Given $\hexpmech(\dataobs)$, then the following property holds:
\begin{equation*}
\hexpmechPr{\dataobs}{\ux{z} = \ux{r}} = \cardinality{\dataobs}{r}\hexpmechPr{\dataobs}{z = r}
 \end{equation*}
\end{lem}
\begin{proof} of Lemma \ref{lem_score_pro_convert}.\\
To compute $\hexpmechPr{\dataobs}{\ux{z} = \ux{r}}$\\
$\iff $ to compute $\hexpmechPr{\dataobs}{ R | R = \{r' | r' \in \candidateset{\dataobs} \land \ux{r'} = \ux{r}\}}.$\\
By Definition \ref{def_cardinality}, $R_r$ is this set.\\
$\implies \hexpmechPr{\dataobs}{\ux{z} = \ux{r}} = \hexpmechPr{\dataobs}{R_r} $.\\
By the independence of $r' \in R_r$, $ \hexpmechPr{\dataobs}{z \in R_r}  =\sum\limits_{r'\in R_r} \hexpmechPr{\dataobs}{z = r'}$ ,\\
Apply Lemma \ref{lem_score_pro_eq} in $R_r$, \\
$\implies$ for any $r', r''\in R_r$, $\hexpmechPr{\dataobs}{z = r'} = \hexpmechPr{\dataobs}{z = r''}$.\\
$\implies$ $\sum\limits_{r'\in R_r} \hexpmechPr{\dataobs}{z = r'} = \cardinality{\dataobs}{r}\hexpmechPr{\dataobs}{z = r}$.\\
$\implies$ $\hexpmechPr{\dataobs}{\ux{z} = \ux{r}} = \cardinality{\dataobs}{r}\hexpmechPr{\dataobs}{z = r}$.\\
\end{proof}

@@

In Beta-binomial system, $\cardinality{\dataobs}{r}$ takes two possible values: $1$, $2$:
\begin{itemize}
  \item[-] $\cardinality{\dataobs}{r} = 1$, $\ux{r} = 0$,  containing only the correct posterior.
  \item[-] $\cardinality{\dataobs}{r} = 2$, $\ux{r} \neq 0$. $R_r$ containing 2 elements by the symmetry property of $\hellinger$.
\end{itemize}

\todo{
In Beta-binomial system, $\cardinality{\dataobs}{r}$ takes two possible values: $1$, $2$. Let $\mathcal{R}_1$, $\mathcal{R}_2$ be a partition of $\candidateset{\dataobs}$:
\begin{itemize}
  \item[*] $\mathcal{R}_1 = \{r | r \in \candidateset{\dataobs}\ s.t.\ \cardinality{\dataobs}{r} = 1\}$.
  \item[*] $\mathcal{R}_2 = \{r | r \in \candidateset{\dataobs}\ s.t.\ \cardinality{\dataobs}{r} = 2\}$.
\end{itemize}
}

Let $\ux{t} = \ux{r} + k$. The proof is given by cases:
\begin{itemize}
  \item {\boldmath$\ux{r} \neq 0$, $\ux{r} + k \neq 0$}. \todo{$r \in \mathcal{R}_2 \land t \in \mathcal{R}_2$} \\
  By $\ux{r} + k \neq 0$, $\cardinality{\dataobs}{t} = 2$. \todo{By $t \in \mathcal{R}_2$, $\cardinality{\dataobs}{t} = 2$}\\
  By $\ux{r} \neq 0 $, $\cardinality{\dataobs}{r} = 2$. \todo{By $r \in \mathcal{R}_2$, $\cardinality{\dataobs}{r} = 2$}\\
  Destruct k:
  \begin{itemize}
    \item  $k \geq 0$: $\implies$\\
      \begin{equation*}
      \begin{split}
      LHS 
      & = \cardinality{\dataobs}{r} \cdot \hexpmechPr{\dataobs}{z = r}     (Apply\ Lemma\ \ref{lem_score_pro_convert})\\
      & = \cardinality{\dataobs}{r} \cdot \frac {exp\big(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs),r)}{2\cdot S(\dataobs)}\big)}{\nomalizer{\dataobs}} 
      (Apply\ Definition\ \ref{def_smoo})\\
      & = \cardinality{\dataobs}{r} \cdot \frac{exp(\frac{-\epsilon \ux{r}}{2 S(\dataobs)})}{\unomalizer{\dataobs}}
      (Apply\ \ux{r} = \hellinger(\bysinfer(\dataobs), r))\\
      & = 2 \cdot \frac{exp(\frac{-\epsilon \ux{r}}{2 S(\dataobs)})}{\unomalizer{\dataobs}}                  (Apply\ \cardinality{\dataobs}{r} = 2)\\
      & = 2 \cdot \frac{exp(\frac{-\epsilon (\ux{r} + k - k)}{2 S(\dataobs)})}{\unomalizer{\dataobs}}\\
      & = 2 \cdot \frac{exp(\frac{-\epsilon (\ux{r} + k)}{2 S(\dataobs)} + \frac{\epsilon k}{2 S(\dataobs)})}{\unomalizer{\dataobs}}\\
      & = 2 \cdot \frac{exp(\frac{-\epsilon (\ux{r} + k)}{2 S(\dataobs)})}{\unomalizer{\dataobs}} \cdot e^{\frac{\epsilon k}{2 S(\dataobs)}}\\
      & = 2 \cdot \frac{exp(\frac{-\epsilon (\ux{t})}{2 S(\dataobs)})}{\unomalizer{\dataobs}} \cdot e^{\frac{\epsilon k}{2 S(\dataobs)}}  (Apply \ \ux{t} = \ux{r} + k)\\
      & = e^{\frac{\epsilon k}{2 S(\dataobs)}} \cdot 2 \cdot \frac {exp\big(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs), t)}{2\cdot S(\dataobs)}\big)}{\nomalizer{\dataobs}} 
      (Apply\ \ux{r} = \hellinger(\bysinfer(\dataobs), r))\\
      & = e^{\frac{\epsilon k}{2 S(\dataobs)}} \cdot 2 \hexpmechPr{\dataobs}{z = t}       (Apply\ Definition\ \ref{def_smoo})\\
      & = e^{\frac{\epsilon k}{2 S(\dataobs)}} \cdot \cardinality{\dataobs}{t} \hexpmechPr{\dataobs}{z = t}         (Apply \ \cardinality{\dataobs}{t} = 2)\\
      & = e^{\frac{\epsilon k}{2 S(\dataobs)}} \cdot \hexpmechPr{\dataobs}{\ux{z} = \ux{t}}               (Apply \ Lemma\ \ref{lem_score_pro_convert})\\
      & = e^{\frac{\epsilon k}{2 S(\dataobs)}} \cdot \hexpmechPr{\dataobs}{\ux{z} = (\ux{r} + k)}         (Apply \ \ux{t} = \ux{r} + k)\\
      & \leq e^{(\frac{\epsilon k}{2 S(\dataobs)} + \ln 2)} \hexpmechPr{\dataobs}{\ux{z} = (\ux{r} + k)}\\
      & = RHS.
      \end{split}
      \end{equation*}

@@

      \begin{equation*}
      \begin{split}
      LHS 
      & = \cardinality{\dataobs}{r} \cdot \hexpmechPr{\dataobs}{z = r}     (Apply\ Lemma\ \ref{lem_score_pro_convert})\\
      & = \cardinality{\dataobs}{r} \cdot \frac {exp\big(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs),r)}{2\cdot S(\dataobs)}\big)}{\nomalizer{\dataobs}} 
      (Apply\ Definition\ \ref{def_smoo})\\
      & = \cardinality{\dataobs}{r} \cdot \frac{exp(\frac{-\epsilon \ux{r}}{2 S(\dataobs)})}{\unomalizer{\dataobs}}
      (Apply\ \ux{r} = \hellinger(\bysinfer(\dataobs), r))\\
      & = 2 \cdot \frac{exp(\frac{-\epsilon \ux{r}}{2 S(\dataobs)})}{\unomalizer{\dataobs}}                  (Apply\ \cardinality{\dataobs}{r} = 2)\\
      & = 2 \cdot \frac{exp(\frac{-\epsilon (\ux{r} + k - k)}{2 S(\dataobs)})}{\unomalizer{\dataobs}}\\
      & = 2 \cdot \frac{exp(\frac{-\epsilon (\ux{r} + k)}{2 S(\dataobs)} + \frac{\epsilon k}{2 S(\dataobs)})}{\unomalizer{\dataobs}}\\
      & = 2 \cdot \frac{exp(\frac{-\epsilon (\ux{r} + k)}{2 S(\dataobs)})}{\unomalizer{\dataobs}} \cdot e^{\frac{\epsilon k}{2 S(\dataobs)}}\\
      & = 2 \cdot \frac{exp(\frac{-\epsilon (\ux{t})}{2 S(\dataobs)})}{\unomalizer{\dataobs}} \cdot e^{\frac{\epsilon k}{2 S(\dataobs)}}  (Apply \ \ux{t} = \ux{r} + k)\\
      & = e^{\frac{\epsilon k}{2 S(\dataobs)}} \cdot 2 \cdot \frac {exp\big(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs), t)}{2\cdot S(\dataobs)}\big)}{\nomalizer{\dataobs}} 
      (Apply\ \ux{r} = \hellinger(\bysinfer(\dataobs), r))\\
      & = e^{\frac{\epsilon k}{2 S(\dataobs)}} \cdot 2 \hexpmechPr{\dataobs}{z = t}       (Apply\ Definition\ \ref{def_smoo})\\
      & = e^{\frac{\epsilon k}{2 S(\dataobs)}} \cdot \cardinality{\dataobs}{t} \hexpmechPr{\dataobs}{z = t}         (Apply \ \cardinality{\dataobs}{t} = 2)\\
      & = e^{\frac{\epsilon k}{2 S(\dataobs)}} \cdot \hexpmechPr{\dataobs}{\ux{z} = \ux{t}}               (Apply \ Lemma\ \ref{lem_score_pro_convert})\\
      & = e^{\frac{\epsilon k}{2 S(\dataobs)}} \cdot \hexpmechPr{\dataobs}{\ux{z} = (\ux{r} + k)}         (Apply \ \ux{t} = \ux{r} + k)\\
      & \leq e^{(\frac{\epsilon k}{2 S(\dataobs)} + \ln 2)} \hexpmechPr{\dataobs}{\ux{z} = (\ux{r} + k)}\\
      & = RHS.
      \end{split}
      \end{equation*}

@@

  \item {\boldmath$\ux{r} = 0, \ux{r} + k \neq 0$}. \todo{$r \in \mathcal{R}_1 \land t \in \mathcal{R}_2$}\\
        By $\ux{r} = 0$, $\cardinality{\dataobs}{r} = 1$. \todo{By $r \in \mathcal{R}_1$, $\cardinality{\dataobs}{t} = 1$}\\
        By $\ux{r} + k = k \neq 0$, $\cardinality{\dataobs}{t} = 2$. \todo{By $t \in \mathcal{R}_2$, $\cardinality{\dataobs}{t} = 2$}\\
        $\implies$\\
        \begin{equation*}
        \begin{split}
        LHS 
        & = \cardinality{\dataobs}{r} \cdot \hexpmechPr{\dataobs}{z = r}     (Apply\ Lemma\ \ref{lem_score_pro_convert})\\
        & = \cardinality{\dataobs}{r} \cdot \frac {exp\big(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs),r)}{2\cdot S(\dataobs)}\big)}{\nomalizer{\dataobs}} 
        (Apply\ Definition\ \ref{def_smoo})\\
        & = \cardinality{\dataobs}{r} \cdot \frac{exp(\frac{-\epsilon \ux{r}}{2 S(\dataobs)})}{\unomalizer{\dataobs}}
        (Apply\ \ux{r} = \hellinger(\bysinfer(\dataobs), r))\\
        & = \frac{exp(\frac{- \epsilon \ux{r}}{2 S(\dataobs)})}{\unomalizer{\dataobs}}                        (Apply \ \cardinality{\dataobs}{r} = 1) \\
        & = \frac{exp(\frac{- \epsilon (\ux{r} + k - k)}{2 S(\dataobs)})}{\unomalizer{\dataobs}}\\
        & = \frac{exp(\frac{- \epsilon (\ux{r} + k)}{2 S(\dataobs)} + \frac{\epsilon k}{2 S(\dataobs)})}{\unomalizer{\dataobs}}\\
        & = \frac{exp(\frac{-\epsilon (\ux{r} + k)}{2 S(\dataobs)})}{\unomalizer{\dataobs}} \cdot e^{\frac{\epsilon k}{2 S(\dataobs)}}\\
        & = \frac{exp(\frac{-\epsilon (\ux{t})}{2 S(\dataobs)})}{\unomalizer{\dataobs}} \cdot e^{\frac{\epsilon k}{2 S(\dataobs)}}  (Apply \ \ux{t} = \ux{r} + k)\\
        & = e^{\frac{\epsilon k}{2 S(\dataobs)}} \cdot \frac {exp\big(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs), t)}{2\cdot S(\dataobs)}\big)}{\nomalizer{\dataobs}} 
        (Apply\ \ux{r} = \hellinger(\bysinfer(\dataobs), r))\\
        & = e^{\frac{\epsilon k}{2 S(\dataobs)}} \cdot \hexpmechPr{\dataobs}{z = t}       (Apply\ Definition\ \ref{def_smoo})\\
        & < 2 \cdot e^{\frac{\epsilon k}{2 S(\dataobs)}} \cdot \hexpmechPr{\dataobs}{z = t}\\
        & = e^{\frac{\epsilon k}{2 S(\dataobs)}} \cdot \cardinality{\dataobs}{t} \hexpmechPr{\dataobs}{z = t}   (Apply \ \cardinality{\dataobs}{t} = 2)\\
        & = e^{\frac{\epsilon k}{2 S(\dataobs)}} \cdot \hexpmechPr{\dataobs}{\ux{z} = \ux{t}}         (Apply \ Lemma\ \ref{lem_score_pro_convert})\\
        & = e^{\frac{\epsilon k}{2 S(\dataobs)}} \cdot \hexpmechPr{\dataobs}{\ux{z} = (\ux{r} + k)}   (Apply \ \ux{t} = \ux{r} + k)\\
        & \leq e^{(\frac{\epsilon k}{2 S(\dataobs)} + \ln 2)} \hexpmechPr{\dataobs}{\ux{z} = ( \ux{r} + k)}\\
        & = RHS.
        \end{split}
        \end{equation*}

  \item {\boldmath$\ux{r} \neq 0, \ux{r} + k = 0$} \todo{$r \in \mathcal{R}_2 \land t \in \mathcal{R}_1$}

      By $\ux{r} + k = 0$, $\cardinality{\dataobs}{t} = 1$. \todo{By $t \in \mathcal{R}_1$, $\cardinality{\dataobs}{t} = 1$}

      By $\ux{r} \neq 0$, $\cardinality{\dataobs}{r} = 2$.  \todo{By $r \in \mathcal{R}_2$, $\cardinality{\dataobs}{t} = 2$}

      $\implies$
      \begin{equation*}
      \begin{split}
      LHS   
      & = \cardinality{\dataobs}{r} \cdot \hexpmechPr{\dataobs}{z = r}     (Apply\ Lemma\ \ref{lem_score_pro_convert})\\
      & = \cardinality{\dataobs}{r} \cdot \frac {exp\big(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs),r)}{2\cdot S(\dataobs)}\big)}{\nomalizer{\dataobs}} 
      (Apply\ Definition\ \ref{def_smoo})\\
      & = \cardinality{\dataobs}{r} \cdot \frac{exp(\frac{-\epsilon \ux{r}}{2 S(\dataobs)})}{\unomalizer{\dataobs}}
      (Apply\ \ux{r} = \hellinger(\bysinfer(\dataobs), r))\\
      & = 2 \cdot \frac{exp(\frac{-\epsilon \ux{r}}{2 S(\dataobs)})}{\unomalizer{\dataobs}}                  (Apply \ \cardinality{\dataobs}{r} = 2)\\
      & = 2 \cdot \frac{exp(\frac{-\epsilon (\ux{r} + k - k)}{2 S(\dataobs)})}{\unomalizer{\dataobs}}\\
      & = 2 \cdot \frac{exp(\frac{-\epsilon (\ux{r} + k)}{2 S(\dataobs)} + \frac{\epsilon k}{2 S(\dataobs)})}{\unomalizer{\dataobs}}\\
      & = 2 \cdot \frac{exp(\frac{-\epsilon (\ux{r} + k)}{2 S(\dataobs)})}{\unomalizer{\dataobs}} \cdot e^{\frac{\epsilon k}{2 S(\dataobs)}}\\
      & = 2 \cdot \frac{exp(\frac{-\epsilon (\ux{t})}{2 S(\dataobs)})}{\unomalizer{\dataobs}} \cdot e^{\frac{\epsilon k}{2 S(\dataobs)}}  (Apply \ \ux{t} = \ux{r} + k)\\
      & = 2 \cdot e^{\frac{\epsilon k}{2 S(\dataobs)}} \cdot \frac {exp\big(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs), t)}{2\cdot S(\dataobs)}\big)}{\nomalizer{\dataobs}} 
      (Apply\ \ux{r} = \hellinger(\bysinfer(\dataobs), r))\\
      & = 2 \cdot e^{\frac{\epsilon k}{2 S(\dataobs)}} \hexpmechPr{\dataobs}{z = t}       (Apply\ Definition\ \ref{def_smoo})\\
      & = 2 \cdot e^{\frac{\epsilon k}{2 S(\dataobs)}} \cdot \cardinality{\dataobs}{t} \hexpmechPr{\dataobs}{z = t} (Apply\ \cardinality{\dataobs}{t} = 1)\\
      & = 2 \cdot e^{\frac{\epsilon k}{2 S(\dataobs)}} \cdot \hexpmechPr{\dataobs}{\ux{z} = \ux{t}}       (Apply \ Lemma\ \ref{lem_score_pro_convert})\\
      & = 2 \cdot e^{\frac{\epsilon k}{2 S(\dataobs)}} \cdot \hexpmechPr{\dataobs}{\ux{z} = (\ux{r} + k)} (Apply \ \ux{t} = \ux{r} + k)\\
      & = e^{\ln 2} \cdot e^{\frac{\epsilon k}{2 S(\dataobs)}} \cdot \hexpmechPr{\dataobs}{\ux{z} = (\ux{r} + k)}\\
      & = e^{(\frac{\epsilon k}{2 S(\dataobs)} + \ln 2)} \hexpmechPr{\dataobs}{\ux{z} = (\ux{r} + k)}\\
      & = RHS.
      \end{split}
      \end{equation*}

  \item {\boldmath $\ux{r} = 0, \ux{r} + k = 0$}: \todo{$r \in \mathcal{R}_1 \land t \in \mathcal{R}_1$}
